Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-07 paper/paper.tex
Initial approximation at Alessandro's request for clear nomenclature (still some work to be done on G(s) and the propagation of errors during synthesis)

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of bits
of the integer and fractional part, respectively.  Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling and holding processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.% {\item \red{[but the ZOH is for the DAC, not for the ADC?]}.

Let $C(z)$ and $G(z)$ transfer functions be arranged in vectors $c_0$ and
$g_0$, respectively.  For each $C(z)$ implementation, there is a function
$\mathit{FWL}[\cdot]:\mathbb{R}^{N_C+M_C}\rightarrow
Q[\mathbb{R}^{N_C+M_C}]$, which applies FWL effects to the controller
$C(z)$, where $Q[\mathbb{R}]$ represents the quantized set of representable
real numbers in the chosen implementation format \param{N_C}{M_C} \red{[clarify this notation]}.  The
quantized controller parameters vector ($c$) is generated via
$\mathit{FWL}[c_0]$.  The uncertain plant parameters ($g$) can be expressed
as
%
\begin{equation}
g = g_0 + \Delta{g} = \left [
				\begin{tabular}{c}
				$b_{0}+\Delta{b_{0}} ~ b_{1}+\Delta{b_{1}} ~ ... ~ b_{M_G}+\Delta{b_{M_G}}$ \\%~ 
				$a_{0}+\Delta{a_{0}} ~ a_{1}+\Delta{a_{1}} ~ ... ~ a_{N_G}+\Delta{a_{N_G}}$
				\end{tabular}
				\right ],
\end{equation}

\vspace{1 mm} 
\noindent where $\Delta{g}$ represents the plant uncertainties coefficients. The polynomial set of possible values of $g$ is denoted by $\mathfrak{G}$.

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $u(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$. \red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct? Let us not mix up the role and the influence of the two blocks.]}
%
\end{myassumption}

>>>>

In this study, the methodology used for verifying closed-loop digital
control system is based on the Digital-System Verifier
(DSVerifier)~\cite{IsmailBCFF15}, which checks the stability of control
systems considering finite-word length (FWL) effects in the digital
controller and uncertainty parameters in the plant model (plant
intervals)~\cite{Bessa16}.  Let $C(z)$ be a digital controller and $G(z)$ be
a plant model given as
%
\begin{align}
\small
\label{controller_plant_tf}
C(z)&=\frac{\beta_{0}+\beta_{1}z^{-1}+...+\beta_{M_C}z^{-M_C}}{\alpha_{0}+\alpha_{1}z^{-1}+...+\alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
G(z)&=\frac{b_{0}+b_{1}z^{-1}+...+b_{M_G}z^{-M_G}}{a_{0}+a_{1}z^{-1}+...+a_{N_G}z^{-N_G}}.
\end{align}
%
\noindent where $\beta$ and $\alpha$ are the controller's coefficients, $b$
and $a$ are the plant's coefficients, and $N$ and $M$ are the number of poles and zeros for the corresponding block.

Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling and holding processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.

Since $G(z)$ is an approximation of $G(s)$ calculated via a discrete z transform using a selected sampling time, we denote the error in the approximation as $\Delta{G}_P$
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z,T)+\Delta{G}_P(z,T).
\end{align}
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined percentage which relates to the nature of the z transform and the sampling time. For simplicity we will use $G(z)$ to represent $G(z,T)$.

Let $\tilde C(z)$ and $\tilde G(z)$ be the same transfer functions represented using a Fixed Point Finite Word Length with integer size $I$ and fractional size $F$. We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ domain, 
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
However, since the plant was originally in the real domain,
\begin{align}
\small
\label{digital_plant_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \nonumber \\
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}

\vspace{1 mm} 
\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by the rounding off effect. We may encompass all the uncertainty as $\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$. Since this value is nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is denoted by $\mathfrak{G}$.

@@

\begin{myassumption}
%
The DAC interpolator is an ideal ZOH; it takes the discrete value of control
signal $u_d(k)$ at instant $k$ and produces a rectangular pulse of height
$u(k)$ and width equal to the sample time $T$. \red{[Right: so under this assumption, we really only focus on the quantisation effects introduced by the ADC, correct? Let us not mix up the role and the influence of the two blocks.]}
%
\end{myassumption}
